### 2019-04-23 Sections/verification_of_cloud_quantum_computing.tex
GI ZKP++

Works for all \textbf{NP}-complete problems.

Alg.~\ref{alg:ZKP_graph}

Fig.~\ref{fig:ZKP_graph}

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{ZKP_graph_isomorphism}
\captionspacefig \caption{The isomorphisms \mbox{$G_1\sim G_2$} (top), and \mbox{$G_1\sim H$} and \mbox{$G_2\sim H$} (bottom). Knowing the latter two isomorphisms simultaneously implies knowledge of \mbox{$G_1\sim G_2$} via composition of the permutations. However, knowing only one of them does not, since $H$ is chosen randomly. By repeatedly proving knowledge of one of the isomorphisms with $H$ we achieve asymptotic certainty that the prover must have known \mbox{$G_1\sim G_2$}, without actually revealing the associated permutation.}\label{fig:ZKP_graph}
\end{figure*}

>>>>

\comment{Ryan's links for NEXP ZKPs.}

\comment{General results.}

\comment{Ryan review.}

A zero-knowledge proof (ZKP) is an interactive protocol\index{Interactive protocols} between two parties -- a \textit{prover}\index{Prover} Peggy, and a \textit{verifier}\index{Verifier} Victor -- where Peggy wishes to efficiently prove to Victor that she knows the solution to a problem, without actually revealing it. Thus, a ZKP can act as a signature that a problem has been faithfully solved, without disclosing the solution.

In the case of classical computing, a variety of free software packages are available for compiling ZKPs for generic code. However, ZKPs become far more valuable in the case of cloud quantum computing, where there is an inherent complexity asymmetry between the client Victor (classical resources only) and the server Peggy (full quantum resources), whereby efficient ZKPs become a useful transactional tool during computational outsourcing.

To illustrate the operation of a ZKP protocol, a conceptually simple example is that of the graph isomorphism\index{Graph isomorphism} problem. Two graphs are \textit{isomorphic}, denoted \mbox{$G_1\sim G_2$}, if there exists a permutation \mbox{$\pi\in S_n$} on their vertex labels that makes them equivalent, i.e \mbox{$G_1=\pi\cdot G_2$}.

This problem is clearly contained in \textbf{NP}, since permuting vertices in graphs and directly comparing them is computationally straightforward, making verification of the problem a polynomial-time affair. However, it is believed that explicitly determining the respective permutation is difficult in general. This is intuitively unsurprising, since for a graph with $n$ vertices, there are $n!$ possible permutations to consider (the order of the symmetric group\index{Symmetric group}, $|S_n|$), and therefore a na{\" i}ve brute-force\index{Brute-force} approach would require $O(n!)$ comparisons in the worst case (of course, in many special cases knowledge of the underlying graph structure can simplify this enormously). This problem is not believed to be contained in either \textbf{P} or \textbf{NP}-complete, and therefore presumed to be \textbf{NP}-intermediate\index{\textbf{NP}-intermediate}.

In the example isomorphism presented in Fig.~\ref{fig:ZKP_graph}(top), the vertex permutation mapping $G_1$ to $G_2$ can be expressed in vector form as,
\begin{align}
\pi = \begin{pmatrix}
	1 \\
	2 \\
	3 \\
	4 \\
	5
\end{pmatrix}_{G_1} \to \begin{pmatrix}
	1 \\
	2 \\
	4 \\
	3 \\
	5
\end{pmatrix}_{G_2},
\end{align}
where indices denote vertex labels, or equivalently via the permutation matrix,
\begin{align}
\pi = \begin{pmatrix}
	1 & 0 & 0 & 0 & 0 \\
	0 & 1 & 0 & 0 & 0 \\
	0 & 0 & 0 & 1 & 0 \\
	0 & 0 & 1 & 0 & 0 \\
	0 & 0 & 0 & 0 & 1
\end{pmatrix}.
\end{align}

In the case of providing a ZKP for graph isomorphism, we imagine a scenario where for two arbitrary isomorphic graphs \mbox{$G_1\sim G_2$}, Peggy wishes to prove to Victor that she knows the associated permutation $\pi$, without revealing what it actually is. An efficient classical ZKP protocol for this problem is explained in Alg.~\ref{alg:ZKP_graph}, and a specific example illustrated in Fig.~\ref{fig:ZKP_graph}.

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{ZKP_graph_isomorphism}
\captionspacefig \caption{The isomorphisms \mbox{$G_1\sim G_2$} (top), and \mbox{$G_1\sim H$} and \mbox{$G_2\sim H$} (bottom). Coloured lines indicate the vertex relabelings associated with the respective isomorphisms. Knowing the latter two isomorphisms simultaneously implies knowledge of \mbox{$G_1\sim G_2$} via composition of the permutations. However, knowing only one of them does not, since $H$ is chosen randomly. By repeatedly proving knowledge of one of the isomorphisms with $H$ we achieve asymptotic certainty that the prover must have known \mbox{$G_1\sim G_2$}, without actually revealing the associated permutation.}\label{fig:ZKP_graph}
\end{figure*}
